Apache Storm

### 2018-01-10 paper.tex
Fixed Resilience details to concepts section

\begin{abstract}
Apache Storm is one of the available open source tools for Stream Data Processing. This document provides a brief overview of the intricacies of the Architecture of Storm and tends to proceed further on the details of considerations required to design a Solution based on Storm. The design considerations relating to deployment of Storm System as a Lambda or a Lambda-less Architecture and the sketch of the various internal components of Storm i.e. Bolts, Spouts. We consider a practical implementation of Storm to try and express the theoretical design considerations in real practice. Finally we list out the other available tools and compare them to Storm with regard to Performance, Resilience and various other parameters.
\end{abstract}

@@

@@

\subsection{System Architecture}
As discussed above, a data processing stream has different requirements and according to these various requirements, the System can be modified to suit the needs. The major two System architectures currently available are the Lambda Architechture and the Lambda-less (or Kappa) Architecture.

@@

\subsubsection{Resilience:} Apache storm includes APIs which allow users to develop solutions which are resilient in nature. Using the acker bolt as show in figure \ref{fig:acker}, users can track the progress of the tuple injected into the system. Thus, writing a spout which can replay the tuple in case of failures allows us to guarantee the processing of data.

@@

\subsection{Storm Resilience}
\label{sec:resilience}

It has two types of processing schemes, \textbf{at least once} where each tuple is processed as the name suggests, at least once, and the other \textbf{at most once}, where the tuples are either processed once or dropped in cases of failure. To provide \textbf{at least once} semantics, Storm maintains an acker bolt, which keeps track of the tuple flow in the directed acyclic graph.

@@

The only spout uses Twitter Hosebird Client (\url{https://github.com/twitter/hbc}) to connect to Twitter Streaming Server and consume the Tweets generated in real time. Whereas the Bolts were programmed in java and the code can be viewed in \url{https://github.com/hakku276/storm-sentiment-analysis}.

@@

\section{Other Tools}
 \label{sec:othertools}
 Stream processing is a topic under constant focus at present and a lot of tools as well as models have been designed and created to support such processing. Apart from Apache storm there are other tools such as, 
 <Describe shortly that other tools are available as well and list them with short descriptions>

@@

@@

\section{Bibliography}
\bibliographystyle{splncs03}
\bibliography{paper}
Alle Links wurden zuletzt am 22.06.2015 geprüft.
\end{document}

>>>>

\begin{abstract}
Apache Storm is one of the available open source tools for Stream Data Processing. This document provides a brief overview of the intricacies of the Architecture of Storm and tends to proceed further on the details of considerations required to design a Solution based on Storm. The design considerations relating to deployment of Storm System as a Lambda or a Lambda-less Architecture and the sketch of the various internal components of Storm i.e. Bolts, Spouts. We consider a practical implementation of Storm to try and express the theoretical design considerations in practice. Finally we list out the other available tools and compare them to Storm with regard to Performance, Resilience and various other parameters.
\end{abstract}

@@

\subsection{Fault Tolerance and Resilience}
\label{sec:resilience}
Apache storm offers fault tolerance and resilience mechanisms with out of the box support and is tolerant against different types of failures. Nimbus, being the main master node, is in-charge of all the other worker nodes. Under the circumstance that a worker node fails, Nimbus re-spawns a worker node and assigns the tasks to this node. If the nimbus itself fails, the nimbus is not re-started automatically, but the worker nodes do not stop processing the stream. The nimbus can be later on restarted manually. During this phase, if a worker fails, it will not be restarted. The supervisor is also an active element within the Storm Architecture and keeps the Nimbus posted about it's current status. The \textbf{heartbeat} event is scheduled to run every 15 seconds and it reports to the Nimbus that the worker node is alive. \cite{stormtwitter}

Apache Storm supports two types of processing schemes, \textbf{at least once} where each tuple is processed as the name suggests, at least once, and the other \textbf{at most once}, where the tuples are either processed once or dropped in cases of failure. To provide \textbf{at least once} semantics, Storm maintains an acker bolt, which keeps track of the tuple flow in the directed acyclic graph.

@@

\subsection{System Architecture}
As discussed above, a data processing stream has different requirements and according to these various requirements, the System can be modified to suit the needs. The major two System architectures currently available are the Lambda Architecture and the Lambda-less (or Kappa) Architecture.

@@

\subsubsection{Resilience:} Apache storm includes APIs which allow users to develop solutions which are resilient in nature. Using the acker bolt as show in figure \ref{fig:acker}, users can track the progress of the tuple injected into the system. Thus, writing a spout which can replay the tuple in case of failures allows us to guarantee the processing of data. For additional details please follow Section \ref{sec:resilience}.

@@

@@

The only spout available in this example uses Twitter Hosebird Client (\url{https://github.com/twitter/hbc}) to connect to Twitter Streaming Server and consume the Tweets generated in real time. Whereas the Bolts were programmed in java and the code can be viewed in \url{https://github.com/hakku276/storm-sentiment-analysis}.

@@

\section{Other Tools}
 \label{sec:othertools}
 Stream processing is a topic under constant focus at present and a lot of tools as well as models have been designed and created to support it. Apart from Apache storm there are other tools such as:

 \begin{enumerate}
 \item \textbf{Spark Streaming} is an Open Source based project for stream processing.  It relies on cluster computing systems and operates on batches. The batch window in Spark Streaming is comparatively small thus allowing stream processing.It also provides flexibility to work in different programming languages such as Java, Scala and Python.
 \item \textbf{Apache Samza} 
 \item \textbf{Yahoo S4} is also a Real time stream processing tool inspired by the MapReduce Model.
 \end{enumerate}

@@

 \subsubsection{Benchmarks}

@@

\section{Bibliography}
\bibliographystyle{splncs03}
\bibliography{paper}
All Links were verified at 10.01.2018
\end{document}
